Modal Abstractions for Virtualizing Memory Addresses

### 2023-11-15 examples.tex

@@

\todo[inline]{typeset as a triple}

>>>>

\begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace}(\ptablestore,m)\stackrel{\triangle}{=} \textsf{ASpace\_Lookup}(\ptablestore,\Xi,m) \ast \\
  \qquad\qquad\qquad \bigast{(\vaddr, \textsf{paddr})\in \ptablestore}{\exists\;(\textsf{l4e, l3e, l2e, l1e, paddr})\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr\textsf{, l4e, l3e, l2e, l1e, paddr})} \\
  \qquad\qquad\qquad \bigast{(\vaddr, \textsf{paddr})\in \Xi}{\exists\; (\textsf{qfrac, val, vaddr}) \ldotp \ulcorner \textsf{vaddr} = \textsf{paddr} + \textsf{KERNBASE} \urcorner \ast  \underbrace{\sumwalkabs\vaddr\qfrac\paddr }_\text{Ghost translation} \ast \\
\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad    \underbrace{\paddr \mapsto_{\mathsf{p}}\{\textsf{qfrac}\}\; \vale}_\text{Physical location} \ast \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner }\\
  \textsf{ where } \\
   \textsf{ASpace\_Lookup} (\ptablestore,m) \stackrel{\triangle}{=} \lambda\textsf{ cr3val} \ldotp \; \exists \gammaPred \; \ldotp \ulcorner m \; !!\; \textsf{cr3val} = \textsf{Some } \gammaPred \urcorner \ast
   \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \\ \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad \ownGhost\gammaPred{\authfull{\ptableabswalk\Xi}}

\end{array}
\]
\caption{Global Address-Space Invariant in Figure \ref{fig:peraspaceinvariant} extended with a ghost map bookkeeping identity mappings }
  \label{fig:peraspaceinvariant_with_p2v_extension}
  \end{figure*}

@@

;; This offsetst physical address at KERNBASE!
add r,  
